---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
## Overview
**dbdataset** is a data package the contains 74 different dataset parsed from [DrugBank](https://www.drugbank.ca) XML database using [dbparser](https://dainanahan.github.io/dbparser/) r package.

These datasets can be used easily as R dataframes to ease the drugs development research  process that might use **DrugBank** database.

However; it also can be used to in Machine Learning in many sub-fields such as:

- Natural Language Processing (NLP)
- Web Scrapping
- Visualization

### Installation
As the package size exceedes CRAN limit it will be hosted on Github only right now. Hence it could be installed via the following command

```{r eval=FALSE}
devtools::install_github("Dainanahan/dbdataset")
```

Then the datasets will be available after the following running the following command
```{r eval=FALSE}
library(dbdataset)
```





