---
title: "dbdataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dbdataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview
**dbdataset** is a data package containing **dvobject** R object. **dvobject**contains lists of different dataframes of the parsed [DrugBank](https://www.drugbank.ca) database. **dvobject** has been built using [dbparser](https://docs.ropensci.org/dbparser) R package.

**dvobject** can be used for conveniently exploring and analyzing the contents of the DrugBank database. **dvobject** is also intended to assist in drug discovery endeavors that plan to make use of the **DrugBank** database.

Moreover; it also can be used to in Machine Learning in many sub-fields such as:

- Natural Language Processing (NLP)
- Web Scrapping
- Visualization

### Installation
Although **dvobject** is much smaller that the unparsed DrugBank database size, it still exceeds the limit set by CRAN. So, it will be hosted on Github only for now. Hence, it could be installed via the following command.

```{r eval=FALSE}
devtools::install_github("interstellar-Consultation-Services/dbdataset")
```

The **dvobject** will then be available after running the following command:

```{r eval=FALSE}
library(dbdataset)
```

Then a **dvobject** called `drugbank` will be available to be used as regular *R* object

### dvobject Structure
dvobject introduces a unified and compressed format of drugs data. It is an R list object that contains one or more of the following sub-lists:

```{r}
names(dbdataset::drugbank)
```
The following is the definition for each sub-list:

#### drugs
A list of data.frames that contain drugs information (i.e. synonyms, classifications, …) and it is the only mandatory list

```{r}
names(dbdataset::drugbank[["drugs"]])
```

#### drugs
A data.frame contains drugs salts information

```{r}
head(dbdataset::drugbank[["salts"]], 5)
```

#### products
A data.frame of commercially available drugs products in the world

```{r}
head(dbdataset::drugbank[["products"]], 5)
```

#### references
A list of data.frames of articles, links and textbooks about drugs or CETT data

```{r}
names(dbdataset::drugbank[["references"]])
```


#### cett
A list of data.frames contain targets, enzymes, carriers and transporters information

```{r}
names(dbdataset::drugbank[["cett"]])
```

### Package Version
The package version will always be the same as the **DrugBank** database used.

