---
title: "dbdataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dbdataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview
**dbdataset** is a data package containing different tibbles that constitute the dataset parsed from  [DrugBank](https://www.drugbank.ca). The dataset was extracted from the DrugBank XML database via [dbparser](https://dainanahan.github.io/dbparser/) R package.

The dataset can be used for conveniently exploring and analyzing the contents of the DrugBank database. The dataset is also intended to assist in drug discovery endeavors that plan to make use of the **DrugBank** database.

Moreover; it also can be used to in Machine Learning in many sub-fields such as:

- Natural Language Processing (NLP)
- Web Scrapping
- Visualization

### Installation
As the package size exceeds the limit set by CRAN, it will be hosted on Github only for now. Hence, it could be installed via the following command.

```{r eval=FALSE}
devtools::install_github("Dainanahan/dbdataset")
```

The datasets will then be available after running the following command:

```{r eval=FALSE}
library(dbdataset)
```

Then the pakages will be available to be used as regular *R* object

```{r}
head(dbdataset::Articles_Drug)
```

```{r}
head(dbdataset::Drugs)
```

```{r}
head(dbdataset::Drugs_Pathway_Drug)
```
The 74 object names are listed in the next section and can be used immediately as any regular R dataframe.

### Package Version
The package version will always be the same as the **DrugBank** database used.

### Naming Convention
Each data frame is named based on its position in DrugBank's data hierarchy. For example:

- `Drugs`: is the master data frame at the root of the hierarchy that contains the list of all drugs in DrugBank.
- `Enzymes_Drug`: is the data frame containing the *enzymes* info pertaining to the drugs in the `Drugs` data frame. In other words,
- `Enzymes:` is a child of `Drug` in the hierarchy (i.e. Drug --> Enzymes).
- `Enzymes_Pathway_Drug`: is the data frame containing the *enzymes* info pertaining to the *pathways* that the drugs in `Drugs` are involved in (i.e. Drug --> Pathways --> Enzymes).

## Dataset Contents
The following are the datasets in our package
```{r echo=FALSE}
data <- vcdExtra::datasets("dbdataset")
DT::datatable(data[, c(1,3)])
```


## Dataset Hierarchy
The following illustrates how the datasets are related to each other:

```{r echo=FALSE, fig.width=10, fig.height=10}
library(data.tree)
library(networkD3)
# search for salts, international-brands
# Main node
build_drug_bank_tree <- function() {
  drug <- Node$new("Drugs")
  drug$AddChild("Groups")
  drug$AddChild("Pharmacology")
  references <- drug$AddChild("References")
  
  references$AddChild("Articles")
  references$AddChild("Books")
  references$AddChild("Links")
  references$AddChild("Attachments")
  
  drug$AddChild("Classification")
  drug$AddChild("Calculated Properties")
  drug$AddChild("Synonyms")
  drug$AddChild("Products")
  drug$AddChild("Mixtures")
  drug$AddChild("Packagers")
  drug$AddChild("Manufacturers")
  drug$AddChild("Prices")
  drug$AddChild("Categories")
  drug$AddChild("Affected Organisms")
  drug$AddChild("Dosages")
  drug$AddChild("ATC")
  drug$AddChild("AHFS")
  drug$AddChild("PDB Entries")
  drug$AddChild("Patents")
  drug$AddChild("PDB Entries")
  drug$AddChild("international_brands")
  drug$AddChild("salts")
  
  interactions <- drug$AddChild("Interactions")
  interactions$AddChild("Food")
  interactions$AddChild("Drugs")
  
  drug$AddChild("Sequences")
  drug$AddChild("Experimental Properties")
  drug$AddChild("External Identifiers")
  drug$AddChild("External Links")
  
  pathways <- drug$AddChild("Pathways")
  pathways$AddChild("Drugs")
  pathways$AddChild("Enzymes")
  
  reactions <- drug$AddChild("Reactions")
  reactions$AddChild("Reactions Enzymes")
  
  drug$AddChild("SNP Effects")
  drug$AddChild("SNP Adverse DRs")
  
  targets <- drug$AddChild("Targets")
  targets$AddChild("Actions")
  
  targets_references <- targets$AddChild("References")
  targets_references$AddChild("Articles")
  targets_references$AddChild("Books")
  targets_references$AddChild("Links")
  targets_references$AddChild("Attachments")
  
  targets_polypeptides <- targets$AddChild("Polypeptides")
  targets_polypeptides$AddChild("External Identifiers")
  targets_polypeptides$AddChild("GO Classifiers")
  targets_polypeptides$AddChild("PFAMS")
  targets_polypeptides$AddChild("Synonyms")
  
  enzymes <- drug$AddChild("Enzymes")
  enzymes$AddChild("Actions")
  enzymes_references <- enzymes$AddChild("References")
  enzymes_references$AddChild("Articles")
  enzymes_references$AddChild("Books")
  enzymes_references$AddChild("Links")
  enzymes_references$AddChild("Attachments")
  enzymes_polypeptides <- enzymes$AddChild("Polypeptides")
  enzymes_polypeptides$AddChild("External Identifiers")
  enzymes_polypeptides$AddChild("GO Classifiers")
  enzymes_polypeptides$AddChild("PFAMS")
  enzymes_polypeptides$AddChild("Synonyms")
  
  carriers <- drug$AddChild("Carriers")
  carriers$AddChild("Actions")
  carriers_references <- carriers$AddChild("References")
  carriers_references$AddChild("Articles")
  carriers_references$AddChild("Books")
  carriers_references$AddChild("Links")
  carriers_references$AddChild("Attachments")
  carriers_polypeptides <- carriers$AddChild("Polypeptides")
  carriers_polypeptides$AddChild("External Identifiers")
  carriers_polypeptides$AddChild("GO Classifiers")
  carriers_polypeptides$AddChild("PFAMS")
  carriers_polypeptides$AddChild("Synonyms")
  
  transporters <- drug$AddChild("Transporters")
  transporters$AddChild("Actions")
  transporters_references <- transporters$AddChild("References")
  transporters_references$AddChild("Articles")
  transporters_references$AddChild("Books")
  transporters_references$AddChild("Links")
  transporters_references$AddChild("Attachments")
  transporters_polypeptides <- transporters$AddChild("Polypeptides")
  transporters_polypeptides$AddChild("External Identifiers")
  transporters_polypeptides$AddChild("GO Classifiers")
  transporters_polypeptides$AddChild("PFAMS")
  transporters_polypeptides$AddChild("Synonyms")
  
  return(drug)
}

radialNetwork(
  ToListExplicit(build_drug_bank_tree(), unname = TRUE))
```



